---
title: "Untitled"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(readxl)
library(sf)
library(rgdal)
library(rgeos)
library(geobr)
library(ggthemes)
```
```

Column {data-width=650}
-----------------------------------------------------------------------

### Chart A

```{r}
df_uf_nivel <- read_csv2("data/uf_nivel.csv", col_names = TRUE,
                          locale = locale(encoding = "ISO-8859-1"), col_types = NULL)
```


```{r}
st_brasil <- readOGR("./data/bra_adm1", "BRA_adm1", encoding = "UTF-8", use_iconv = TRUE) 
```

```{r}
sf_brasil <- gSimplify(st_brasil, tol = 0.05, topologyPreserve = TRUE) %>%
  st_as_sf() %>% 
  mutate(UF=st_brasil@data$NAME_1)
```

```{r}
sf_brasil_nivel <- sf_brasil %>% 
  left_join(df_uf_nivel, by = "UF")
```

```{r}
df_estados_indice <- read_csv2("data/uf_nivel.csv", col_names = TRUE,
                          locale = locale(encoding = "ISO-8859-1"), col_types = NULL)
```

```{r}
df_estados <- read_state(year=2018) %>% 
   rename("UF" = name_state) %>% 
  mutate(UF=str_replace_all(UF, " De "," de ")) %>% 
  mutate(UF=str_replace_all(UF, " Do "," do "))
```

```{r}
df_brasil_indice <- df_estados %>% 
  left_join(df_estados_indice, by = "UF")
```

Column {data-width=350}
-----------------------------------------------------------------------

### Chart B

Desenha o mapa
```{r}
sf_brasil_nivel %>% 
  ggplot() +
  geom_sf(aes(fill = Nivel)) +
  coord_sf()
```

### Chart C

```{r}
my_colors <- (c(alto = "red", estavel = "yellow", baixo = "green"))
df_brasil_indice %>% 
  ggplot() +
  geom_sf(aes(fill = Nivel)) +
  scale_fill_manual(name = "Nível", values = my_colors) +
  theme_map() + 
    labs(x = NULL, 
         y = NULL,
         title = "Índice de infecção por COVID-19 no Brasil")

```

